Do moral communities have a spatial dimension? A spatial exploratory analysis of places of worship and violent crime in the city of Recife, Brazil

### 2019-10-16 Moral_Communities_and_Crime_Title_Page_v1.tex
Repeated initial submission after including statements re. funding information and conflicts of interest

\title{Do moral communities have a spatial dimension? A spatial exploratory
analysis of places of worship and violent crime in the city of Recife,
Brazil \thanks{Grants or other notes about the article that should go on the front page
should be placed here. General acknowledgments should be placed at the
end of the article.} }

>>>>

\title{Do moral communities have a spatial dimension? A spatial exploratory
analysis of places of worship and violent crime in the city of Recife,
Brazil \thanks{\textbf{Funding:} Edivaldo Constantino das Neves Júnior received support
from the Government of Canada, through the program Emerging Leaders in
the Americas. \textbf{Conflicts of Interest:} The authors declare that
they have no conflict of interest.} }
